\documentclass[10pt, oneside]{article}
\usepackage{amsmath, amsthm, amssymb, calrsfs, wasysym, verbatim, bbm, color, graphics, geometry}
\usepackage{graphicx}
\graphicspath{ {./assets/} }
\geometry{tmargin=.75in, bmargin=.75in, lmargin=.75in, rmargin = .75in}

\newcommand{\R}{\mathbb{R}}
\newcommand{\C}{\mathbb{C}}
\newcommand{\Z}{\mathbb{Z}}
\newcommand{\N}{\mathbb{N}}
\newcommand{\Q}{\mathbb{Q}}
\newcommand{\Cdot}{\boldsymbol{\cdot}}

\newtheorem{thm}{Theorem}
\newtheorem{defn}{Definition}
\newtheorem{conv}{Convention}
\newtheorem{rem}{Remark}
\newtheorem{lem}{Lemma}
\newtheorem{cor}{Corollary}
\usepackage[backend=biber,style=authoryear]{biblatex}
\addbibresource{reference.bib}

\title{Summary Report: Candidate literary paper to be used}
\author{Alejandro Ouslan}
\date{2026-02-08}

\begin{document}
e
\maketitle
\tableofcontents

\vspace{.25in}

\section*{Paper 1: On the four types of weight functions for spatial contiguity matrix}

\subsection*{Summary}
The studies of spatial complexity have resulted in new understanding of the distance-decay functions of geography.
The weight functions of spatial autocorrelation should be consistent with the functions of spatial distribution and
interaction. This paper is on “spatial autocorrelation analysis” of spatial autocorrelation. The 1-dimension spatial
autocorrelation function (ACF) and partial autocorrelation function (PACF) of space series are employed to analyze four
kinds of weight function in common use for the 2-dimensional spatial autocorrelation model. The aim of this study is
at how to select a proper weight function to construct a spatial contiguity matrix for spatial analysis. The scopes
of application of different weight functions are defined in terms of the characters of their ACFs and PACFs. \cite{chen2012four}

\subsection*{Metadata}
\begin{enumerate}
	\item \textbf{Link:} https://link.springer.com/article/10.1007/s12076-011-0076-6
	\item \textbf{Journal Name:} Letters in Spatial and Resource Sciences
	\item \textbf{Rank:} Q2
\end{enumerate}

\subsection*{Conclusions}
\begin{itemize}
	\item \textbf{Objective:} To provide an objective criterion for selecting spatial weight functions based on the
	      consistency between spatial distribution, interaction, and scale.
	\item \textbf{Methodology:} The author uses 1-dimensional Autocorrelation Functions (ACF) and Partial Autocorrelation
	      Functions (PACF) to analyze the behavior and "spatial memory" of four common weight functions used in
	      2-dimensional spatial analysis.
	\item \textbf{Key Findings:}
	      \begin{itemize}
		      \item Weight functions must match the underlying geographical process (e.g., power-law vs. exponential distributions).
		      \item The choice of function is critical at "critical states" (the transition between chaos and order), where different
		            functions yield significantly different analytical results.
	      \end{itemize}
	\item \textbf{Conclusion:}
	      \begin{itemize}
		      \item \textbf{Power functions} are best for large-scale complex systems.
		      \item \textbf{Exponential functions} suit medium-to-small scale simple systems.
		      \item \textbf{Step functions} are ideal for local-level analysis and negative correlation patterns.
	      \end{itemize}
\end{itemize}

\section*{Paper 2: Autoregressive Spatial Smoothing and Temporal \\Spline Smoothing for Mapping Rates}

\subsection*{Summary}
This article proposes generalized additive mixed models for the analysis of geographic and temporal variability of mortality rates.
This class of models accommodates random spatial effects and fixed and random temporal components. Spatiotemporal models that
use autoregressive local smoothing across the spatial dimension and B-spline smoothing over the temporal dimension are developed.
The objective is the identification of temporal trends and the production of a series of smoothed maps from which spatial patterns
of mortality risks can be monitored over time. Regions with consistently high rate estimates may be followed for further investigation.
The methodology is illustrated by analysis of British Columbia infant mortality data. \cite{macnab2001autoregressive}
\cite{chen2012four}

\subsection*{Metadata}
\begin{enumerate}
	\item \textbf{Link:}  https://doi.org/10.1111/j.0006-341X.2001.00949.x
	\item \textbf{Journal Name:} Biometrics Journal of the international Biometric society
	\item \textbf{Rank:} Q1
\end{enumerate}

\section*{Paper 3: On confidence intervals for generalized additive models based on
  penalized regression splines}

\subsection*{Summary}
Generalized additive models represented using low rank penalized regression splines, estimated by penalized likelihood
maximisation and with smoothness selected by generalized cross validation or similar criteria, provide a computationally
efficient general framework for practical smooth modelling. Various authors have proposed approximate Bayesian interval
estimates for such models, based on extensions of the work of Wahba, G. (1983)[Bayesian confidence intervals for the
		cross validated smoothing spline. J. R. Statist. Soc. B45, 133–150] and Silverman, B.W. (1985)[Some aspects of the spline
		smoothing approach to nonparametric regression curve fitting. J. R. Statist. Soc. B47, 1–52] on smoothing spline
models of Gaussian data, but testing of such intervals has been rather limited and there is little supporting
theory for the approximations used in the generalized case. This paper aims to improve this situation by providing
simulation tests and obtaining asymptotic results supporting the approximations employed for the generalized case.
The simulation results suggest that while across-the-model performance is good, component-wise coverage probabilities
are not as reliable. Since this is likely to result from the neglect of smoothing parameter variability, a simple and
efficient simulation method is proposed to account for smoothing parameter uncertainty: this is demonstrated to
substantially improve the performance of component-wise intervals. \cite{wood2006confidence}

\subsection*{Metadata}
\begin{enumerate}
	\item \textbf{Link:}  https://doi.org/10.1111/j.1467-842X.2006.00450.x
	\item \textbf{Journal Name:} Australian Statistical Publishing Association
	\item \textbf{Rank:} Q3
\end{enumerate}

\section*{Paper 4: GAMs with integrated model selection using penalized regression
  splines and applications to environmental modelling}

\subsection*{Summary}
Generalized additive models (GAMs) have been popularized by the work of Hastie and Tibshirani (Generalized Additive Models (1990))
and the availability of user friendly gam software in Splus. However, whilst it is flexible and efficient, the gam framework
based on backfitting with linear smoothers presents some difficulties when it comes to model selection and inference. On the
other hand, the mathematically elegant work of Wahba (Spline Models for Observational Data (1990)) and co-workers on Generalized
Spline Smoothing (GSS) provides a rigorous framework for model selection (SIAM J. Sci. Statist. Comput. 12 (1991) 383) and
inference with GAMs constructed from smoothing splines: but unfortunately these models are computationally very expensive
with operations counts that are of cubic order in the number of data. A ‘middle way’ between these approaches is to construct
GAMs using penalized regression splines (e.g. Marx and Eilers, Comput. Statist. Data Anal. (1998)). In this paper, we develop
this idea further and show how GAMs constructed using penalized regression splines can be used to get most of the practical
benefits of GSS models, including well founded model selection and multi-dimensional smooth terms, with the ease of use and
low computational cost of backfit GAMs. Inference with the resulting methods also requires slightly fewer approximations
than are employed in the GAM modelling software provided in Splus. This paper presents the basic mathematical and numerical
approach to GAMs implemented in the R package mgcv, and includes two environmental examples using the methods as implemented
in the package.
\cite{wood2002gams}

\subsection*{Metadata}
\begin{enumerate}
	\item \textbf{Link:} https://doi.org/10.1016/S0304-3800(02)00193-X
	\item \textbf{Journal Name:} Ecological modelling
	\item \textbf{Rank:} Q1
\end{enumerate}

\section*{Paper 5: Thin Plate Regression Splines}

\subsection*{Summary}
I discuss the production of low rank smoothers for $d \ge 1$ dimensional data, which can be fitted by regression or penalized
regression methods. The smoothers are constructed by a simple transformation and truncation of the basis that arises from the
solution of the thin plate spline smoothing problem and are optimal in the sense that the truncation is designed to result in
the minimum possible perturbation of the thin plate spline smoothing problem given the dimension of the basis used to construct
the smoother. By making use of Lanczos iteration the basis change and truncation are computationally efficient. The smoothers
allow the use of approximate thin plate spline models with large data sets, avoid the problems that are associated with ‘knot
placement’ that usually complicate modelling with regression splines or penalized regression splines, provide a sensible way
of modelling interaction terms in generalized additive models, provide low rank approximations to generalized smoothing spline
models, appropriate for use with large data sets, provide a means for incorporating smooth functions of more than one variable
into non-linear models and improve the computational efficiency of penalized likelihood models incorporating thin plate splines.
Given that the approach produces spline-like models with a sparse basis, it also provides a natural way of incorporating
unpenalized spline-like terms in linear and generalized linear models, and these can be treated just like any other model
terms from the point of view of model selection, inference and diagnostics.
\cite{wood2003thin}

\subsection**{Metadata}
\begin{enumerate}
	\item \textbf{Link:} https://doi.org/10.1111/1467-9868.00374
	\item \textbf{Journal Name:} Journal of the Royal Statistical Society Series B: Statistical Methodology
	\item \textbf{Rank:} Q1
\end{enumerate}


\section*{Paper 6: Selecting the number of knots for penalized splines}

\subsection*{Summary}
Penalized splines, or P-splines, are regression splines fit by least-squares with a roughness penalty.P-splines have much in
common with smoothing splines, but the type of penalty used with a P-spline is somewhat more general than for a smoothing spline.
Also, the number and location of the knots of a P-spline is not fixed as with a smoothing spline. Generally, the knots of a
P-spline are at fixed quantiles of the independent variable and the only tuning parameters to choose are the number of knots
and the penalty parameter. In this article, the effects of the number of knots on the performance of P-splines are studied.
Two algorithms are proposed for the automatic selection of the number of knots. The myopic algorithm stops when no improvement
in the generalized cross-validation statistic (GCV) is noticed with the last increase in the number of knots. The full search
examines all candidates in a fixed sequence of possible numbers of knots and chooses the candidate that minimizes GCV.The
myopic algorithm works well in many cases but can stop prematurely. The full-search algorithm worked well in all examples
examined. A Demmler–Reinsch type diagonalization for computing univariate and additive P-splines is described. The
Demmler–Reinsch basis is not effective for smoothing splines because smoothing splines have too many knots. For P-splines,
however, the Demmler–Reinsch basis is very useful for super-fast generalized cross-validation.
\cite{ruppert2002selecting}

\subsection*{Metadata}
\begin{enumerate}
	\item \textbf{Link:} https://doi.org/10.1198/106186002853
	\item \textbf{Journal Name:} Journal of computational and graphical statistics
	\item \textbf{Rank:} Q1
\end{enumerate}

\section*{Paper 7: A review of performance criteria to validate simulation models}

\subsection*{Summary}
This study reviews performance criteria adequate to validate simulation models through the comparison of two quantitative
data sets, concerning historical and simulated data. The criteria reviewed were organized according to its characteristics
into the groups: error-based measures, information theory measures, information criteria, parametric tests, non-parametric
tests, distance-based measures and combined measures. Each criterion is reviewed through its mathematic definition, its
applications in literature and the identification of its advantages and drawbacks. The features assessed by each criterion
are identified and discussed. This study provides a concise outline over the criteria reviewed, which can be used as a guide
to help developers of simulation models into the decision on the most appropriate criteria to validate their models.
\cite{hora2015review}

\subsection*{Metadata}
\begin{enumerate}
	\item \textbf{Link:} https://doi.org/10.1111/exsy.12111
	\item \textbf{Journal Name:} Expert Systems
	\item \textbf{Rank:} Q1
\end{enumerate}


\section*{Template}

\subsection*{Summary}
\cite{chen2012four}

\subsection*{Metadata}
\begin{enumerate}
	\item \textbf{Link:}
	\item \textbf{Journal Name:}
	\item \textbf{Rank:}
\end{enumerate}

\subsection*{Conclusions}


\printbibliography
\end{document}
